Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-18 cordillera-cycle.tex
Stroeven et al 2014 has been published.

For more than a century, exploration and geological investigation of the
Cordillera have led to a large collection of evidence of the former ice cover
\citep{Jackson.Clague.1991}. This evidence consists of mapped boundaries of the
former ice extent (\citealp[Fig.~1.12]{Clague.1989}; \citealp{Duk-Rodkin.1999};
\citealp{Dyke.2004}), directions of past sliding velocities
(\citealp{Prest.etal.1968}; \citealp[Fig.~2]{Kleman.etal.2010}), and locations
of former
melt-water streams \citep{Margold.etal.2011, Margold.etal.2013a}, as well as the
timing of glaciation identified from radiocarbon dating \citep[e.g.,][]
{Clague.1981, Porter.Swanson.1998}, cosmogenic dating \citep[e.g.,][]
{Ward.etal.2007, Menounos.etal.2008, Stroeven.etal.2010, Stroeven.etal.2013},
and the offshore sedimentary record \citep{Cosma.etal.2008, Davies.etal.2011}%
\footnote{\textbf{Arjen, Martin,}, please comment on my choice of references
    in this paragraph. Is it a fair sample of the current state of the field?
    Am I missing some other important works?}.

>>>>

For more than a century, exploration and geological investigation of the
Cordillera have led to a large collection of evidence of the former ice cover
\citep{Jackson.Clague.1991}. This evidence consists of mapped boundaries of the
former ice extent (\citealp[Fig.~1.12]{Clague.1989}; \citealp{Duk-Rodkin.1999};
\citealp{Dyke.2004}), directions of past sliding velocities
(\citealp{Prest.etal.1968}; \citealp[Fig.~2]{Kleman.etal.2010}), and locations
of former
melt-water streams \citep{Margold.etal.2011, Margold.etal.2013a}, as well as the
timing of glaciation identified from radiocarbon dating \citep[e.g.,][]
{Clague.1981, Porter.Swanson.1998}, cosmogenic dating \citep[e.g.,][]
{Ward.etal.2007, Menounos.etal.2008, Stroeven.etal.2010, Stroeven.etal.2014},
and the offshore sedimentary record \citep{Cosma.etal.2008, Davies.etal.2011}%
\footnote{\textbf{Arjen, Martin,}, please comment on my choice of references
    in this paragraph. Is it a fair sample of the current state of the field?
    Am I missing some other important works?}.
